Supplementary Analyses

### 2023-02-06 drafting_supplementary_analysis.Rmd
fixed plots

# p value
all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)

@@

@@

# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
# 
# #### identify countries with small samples
# male_length <- function(x){sum(x$sex3=='male')}
# males <- lapply(x, male_length)
# female_length <- function(x){sum(x$sex3=='female')}
# females <- lapply(x, female_length)
# names(females)
# 
# #### generate a vector containing all countries with less than 10 observations for either males or females ####
# exclusions <- c(names(males[males<2]),
#   names(females[females<2]))
# 
# #### re-load ungrouped data ####
# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# 
# # and remove missing again
# sum(is.na(x$moral_identity_internal))
# x <- x[which(is.na(x$moral_identity_internal)==FALSE),]
# 
# #### Filter out any countries to be excluded ####
# x <- subset(x, !(country_name %in% exclusions))
# 
# df1 <- x
# 
# df1_male <- df1[which(df1$sex3=="male"),]
# df1_female <- df1[which(df1$sex3=="female"),]
# 
# internal_mean_sd <- function(x){
#   z <- x
#   z$mean <- mean(z$moral_identity_internal, na.rm=T)
#   z$sd <- sd(z$moral_identity_internal, na.rm=T)
#   z
# }
# 
# 
# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )
# 
# df1$sex3 <- dplyr::recode(df1$sex3
#                            , "male" = "Male"
#                            , "female" = "Female")
# 
# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_internal))+
#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
#   geom_violin(fill = NA) +
#   #ggforce::geom_sina(size=.01)+
#   # geom_sina(shape=16
#   #           , position=position_jitter(height=.25,width=0)
#   #           , size=.000001
#   #           , color="dark grey"
#   #           ,jitter_y=F
#   # )+
#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
#                 position=position_dodge(0.05), color="#5a5a5a")+
#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
#   # stat_summary(geom = "linerange",
#   #   fun.data = mean_sdl,
#   #   fun.args = list(mult = 1),
#   #   colour = "black"
#   # )+
#   xlab("Gender")+
#   ylab("Internalization")+
#   facet_wrap(~df1$ISO3, ncol = 9 )+
#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
#   theme_bw() +
#   theme(panel.border = element_blank(),
#         axis.line = element_line(size = .2),
#         strip.background  = element_blank(),
#         panel.grid = element_blank(),
#         plot.title=element_text(#family="Times",
#           size=12
#         ),
#         #legend.position="right",
#         legend.text=element_text(#family="Times",
#           size=8
#         ),
#         legend.title=element_text(#family="Times",
#           size=10
#         ),
#         axis.text=element_text(#family="Times",
#           colour = "black",
#           size=8
#         ),
#         axis.ticks.x = element_blank(),
#         axis.title=element_text(#family="Times",
#           size=12
#         ),
#         strip.text=element_text(#family = "Times",
#           size = 12
#         ),
#         # strip.background = element_rect(fill = "white"),
#         legend.position="none")
# 
# ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

@@

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)

@@

# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
# 
# #### identify countries with small samples
# male_length <- function(x){sum(x$sex3=='male')}
# males <- lapply(x, male_length)
# female_length <- function(x){sum(x$sex3=='female')}
# females <- lapply(x, female_length)
# names(females)
# 
# #### generate a vector containing all countries with less than 10 observations for either males or females ####
# exclusions <- c(names(males[males<2]),
#   names(females[females<2]))
# 
# #### re-load ungrouped data ####
# x <- df[which(df$sex3=="male"|df$sex3=="female"),]
# x$sex3 <- droplevels(x$sex3)
# 
# # and remove missing again
# sum(is.na(x$moral_identity_symbolic))
# x <- x[which(is.na(x$moral_identity_symbolic)==FALSE),]
# 
# #### Filter out any countries to be excluded ####
# x <- subset(x, !(country_name %in% exclusions))
# 
# df1 <- x
# 
# df1_male <- df1[which(df1$sex3=="male"),]
# df1_female <- df1[which(df1$sex3=="female"),]
# 
# internal_mean_sd <- function(x){
#   z <- x
#   z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
#   z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
#   z
# }
# 
# 
# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )
# 
# df1$sex3 <- dplyr::recode(df1$sex3
#                            , "male" = "Male"
#                            , "female" = "Female")
# 
# g1 <- ggplot(df1,aes(x=sex3,y=moral_identity_symbolic))+
#   #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
#   geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
#   geom_violin(fill = NA) +
#   #ggforce::geom_sina(size=.01)+
#   # geom_sina(shape=16
#   #           , position=position_jitter(height=.25,width=0)
#   #           , size=.000001
#   #           , color="dark grey"
#   #           ,jitter_y=F
#   # )+
#   geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
#   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.06,
#                 position=position_dodge(0.05), color="#5a5a5a")+
#   stat_summary(fun=mean, geom="point", shape=16, size=.5)+
#   # stat_summary(geom = "linerange",
#   #   fun.data = mean_sdl,
#   #   fun.args = list(mult = 1),
#   #   colour = "black"
#   # )+
#   xlab("Gender")+
#   ylab("Symbolization")+
#   facet_wrap(~df1$ISO3, ncol = 9 )+
#   #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
#   theme_bw() +
#   theme(panel.border = element_blank(),
#         axis.line = element_line(size = .2),
#         strip.background  = element_blank(),
#         panel.grid = element_blank(),
#         plot.title=element_text(#family="Times",
#           size=12
#         ),
#         #legend.position="right",
#         legend.text=element_text(#family="Times",
#           size=8
#         ),
#         legend.title=element_text(#family="Times",
#           size=10
#         ),
#         axis.text=element_text(#family="Times",
#           colour = "black",
#           size=8
#         ),
#         axis.ticks.x = element_blank(),
#         axis.title=element_text(#family="Times",
#           size=12
#         ),
#         strip.text=element_text(#family = "Times",
#           size = 12
#         ),
#         # strip.background = element_rect(fill = "white"),
#         legend.position="none")
# 
# #g1
# 
# ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
# #g2
```

@@

>>>>

# p value
all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
raw_ps_for_table <- (lapply(all_t_tests, all_t_ps))

@@

test <- 
  cbind.data.frame(
     round(do.call(rbind, female_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, male_means),digits=2)
    ,round(do.call(rbind, female_sds),digits=2)
    ,round(do.call(rbind, ts_for_table),digits=2)
    ,round(do.call(rbind, df_for_table),digits=2)
    ,do.call(rbind, raw_ps_for_table)
    ,round(do.call(rbind, ds_for_table),digits=2)
    )

sig_countries <- rownames(test[which(test$p<.05),])
```

@@

x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

df1 <- x

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

internal_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_internal, na.rm=T)
  z$sd <- sd(z$moral_identity_internal, na.rm=T)
  z
}

# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

N_fun <- function(x){
  length(x$sex3)
}
length(df1$sex3)
x <- df1
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1 <- left_join(df1
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, N_fun))
                          ,names(unlist(lapply(x, N_fun))))
                        ,c("N","country_name"))
                      , by = "country_name")

df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N, ")"))

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

# x <- df1
# 
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

means_fun <- function(x){
  mean(x$moral_identity_internal)
}
sd_fun <- function(x){
  sd(x$moral_identity_internal)
}

x <- df1_male
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

x <- df1_female
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

df2 <- rbind.data.frame(df1_male,df1_female)

df2$sex3 <- dplyr::recode(df2$sex3
                           , "male" = "Male"
                           , "female" = "Female")

g1 <- ggplot(df2,aes(x=sex3,y=moral_identity_internal))+
  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=means - sds, ymax = means + sds), width=.06,
                position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=1)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl,
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+
  facet_wrap(~df2$country_name3, ncol = 9 )+
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/internalization.png", g1, width = 40, height = 25, units = "in", dpi = 300)

@@

all_t_ps <- function(t){
  t$p.value
}
ps_for_table <- lapply((lapply(all_t_tests, all_t_ps)), ps)
raw_ps_for_table <- (lapply(all_t_tests, all_t_ps))

@@

x <- df[which(df$sex3=="male"|df$sex3=="female"),]
x$sex3 <- droplevels(x$sex3)
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

df1 <- x

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

internal_mean_sd <- function(x){
  z <- x
  z$mean <- mean(z$moral_identity_symbolic, na.rm=T)
  z$sd <- sd(z$moral_identity_symbolic, na.rm=T)
  z
}

# df1 <- rbind.data.frame(
#   internal_mean_sd(df1_female),
#   internal_mean_sd(df1_male)
# )

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

N_fun <- function(x){
  length(x$sex3)
}
length(df1$sex3)
x <- df1
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1 <- left_join(df1
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, N_fun))
                          ,names(unlist(lapply(x, N_fun))))
                        ,c("N","country_name"))
                      , by = "country_name")

df1$country_name3 <- print(paste0(df1$country_name2, " (N = ", df1$N,")"))

df1_male <- df1[which(df1$sex3=="male"),]
df1_female <- df1[which(df1$sex3=="female"),]

# x <- df1
# 
# x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )

means_fun <- function(x){
  mean(x$moral_identity_symbolic)
}

sd_fun <- function(x){
  sd(x$moral_identity_symbolic)
}

x <- df1_male
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_male <- left_join(df1_male
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

x <- df1_female
x <- x %>% group_by(country_name) %>% do(data = (.)) %>% with( set_names(data, country_name) )
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, means_fun))
                          ,names(unlist(lapply(x, means_fun))))
                        ,c("means","country_name"))
                      , by = "country_name")
df1_female <- left_join(df1_female
                      ,  
                      `colnames<-`(
                        cbind.data.frame(
                          unlist(lapply(x, sd_fun))
                          ,names(unlist(lapply(x, sd_fun))))
                        ,c("sds","country_name"))
                      , by = "country_name")

df2 <- rbind.data.frame(df1_male,df1_female)

df2$sex3 <- dplyr::recode(df2$sex3
                           , "male" = "Male"
                           , "female" = "Female")

g1 <- ggplot(df2,aes(x=sex3,y=moral_identity_symbolic))+
  #geom_jitter(height = .1, width = .1, size=.0001, color="gray") +
  geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.1, color="darkgrey")+
  geom_violin(fill = NA) +
  #ggforce::geom_sina(size=.01)+
  # geom_sina(shape=16
  #           , position=position_jitter(height=.25,width=0)
  #           , size=.000001
  #           , color="dark grey"
  #           ,jitter_y=F
  # )+
  geom_boxplot(width=0.1, outlier.shape = NA, color='grey')+
  geom_errorbar(aes(ymin=means - sds, ymax = means + sds), width=.06,
                position=position_dodge(0.05), color="#5a5a5a")+
  stat_summary(fun=mean, geom="point", shape=16, size=1)+
  # stat_summary(geom = "linerange",
  #   fun.data = mean_sdl,
  #   fun.args = list(mult = 1),
  #   colour = "black"
  # )+
  xlab("Gender")+
  ylab("Internalization")+
  facet_wrap(~df2$country_name3, ncol = 9 )+
  #geom_jitter(shape=16, position=position_jitter(height = .5, width = .45), size=.01, color="dark grey")
  theme_bw() +
  theme(panel.border = element_blank(),
        axis.line = element_line(size = .2),
        strip.background  = element_blank(),
        #panel.grid = element_blank(),
        plot.title=element_text(#family="Times",
          size=12
        ),
        #legend.position="right",
        legend.text=element_text(#family="Times",
          size=8
        ),
        legend.title=element_text(#family="Times",
          size=10
        ),
        axis.text=element_text(#family="Times",
          colour = "black",
          size=8
        ),
        axis.ticks.x = element_blank(),
        axis.title=element_text(#family="Times",
          size=12
        ),
        strip.text=element_text(#family = "Times",
          size = 12
        ),
        # strip.background = element_rect(fill = "white"),
        legend.position="none")

ggsave("plots/symbolization.png", g1, width = 40, height = 25, units = "in", dpi = 300)
#g2
```

@@

test <- 
  cbind.data.frame(
     round(do.call(rbind,mean_age_for_table),digits = 2)
    ,round(do.call(rbind,sd_age_for_table),digits = 2)
    ,round(do.call(rbind,mean_int_for_table),digits = 2)
    ,round(do.call(rbind,sd_int_for_table),digits = 2)
    ,round(do.call(rbind, Ns_for_table))
    ,round(do.call(rbind, rs_for_table),digits=3)
    ,do.call(rbind, ps_for_table)
    )

sig_countries <- rownames(test[which(test$p<.05),])

# loop_sigs_fun <- function(x){
#   if(rownames(test)[x] %in% sig_countries) print(paste0(rownames(test)[x],"*"),quote = FALSE)
#   else print(rownames(test)[x])
# }
# 
# rownames(test) <-  unlist(lapply(1:length(rownames(test)), loop_sigs_fun))
# 
# loop_sigs_fun2 <- function(x,y){
#   if(x$country_name[y] %in% sig_countries) print(paste0(x$country_name[y],"*"),quote = FALSE)
#   else print(x$country_name[y])
# }

df1 <- subset(df, !(country_name %in% exclusions))

loop_sigs_fun3 <- function(y){
  if(df1$country_name[y] %in% sig_countries) print(paste0(df1$country_name[y],"*"),quote = FALSE)
  else print(df1$country_name[y])
}

df1$country_name2 <- unlist(lapply(1:length(df1$country_name),loop_sigs_fun3))

ggplot(df1, aes(age, moral_identity_internal))+
  geom_jitter(size=.05, color='darkgrey') + 
  #ylim(0,12) +
  geom_smooth(method=lm, size = .5,color='black') +
  labs(y = "Internalization",
       x = "Age"
  )+ 
  theme_apa()+
  theme_bw()+
  theme(plot.title=element_text(#family="Times",
    size=12
  ),
  legend.text=element_text(#family="Times",
    size=8
  ),
  legend.title=element_text(#family="Times",
    size=10
  ),
  axis.text=element_text(#family="Times",
    colour = "black",
    size=8
  ),
  axis.ticks.x = element_blank(),
  axis.title=element_text(#family="Times",
    size=12
  ),
  strip.text=element_text(#family = "Times",
    size = 12
  ),
  strip.background = element_rect(fill = "white"),
  legend.position="right")+
  facet_wrap(~df1$country_name2, ncol = 9 )
```
